Details of specific functions

### 2020-09-25 inst/gitbook/03_specific-tutorials.Rmd

>>>>

> DISCLAIMER: this method of analysing disparity has not been published yet and has not been peer reviewed. Caution should be used in interpreting these results: it is unclear what "a disparity curve fitting a Brownian motion" actually means biologically.

As Malcolm said in Jurassic Park: "although the examples within this chapter all work and produce solid tested results (from an algorithm point of view), that doesn't mean you should use it" (or something along those lines).
